---
title: "Linear Regression Mini Project"
output: html_document
---

# Load the states data
# ────────────────────────

# read the states data
```{r}
states.data <- readRDS("dataSets/states.rds") 
```

## Exercise: least squares regression
## ────────────────────────────────────────

##   Use the /states.rds/ data set. Fit a model predicting energy consumed
##   per capita (energy) from the percentage of residents living in
##   metropolitan areas (metro). Be sure to
##   1. Examine/plot the data before fitting the model
```{r}

sts.en.me <- states.data %>% select(expense, metro)
plot(sts.en.me)
```

##   2. Print and interpret the model `summary'
```{r}
ex.me.mod <- lm(expense ~ metro, data = states.data)
summary(ex.me.mod)
```

##   3. `plot' the model to look for deviations from modeling assumptions
```{r}
plot(ex.me.mod)
ex.me.mod1 <- lm(energy ~ metro, data = states.data)
plot(ex.me.mod1)
```

##   Select one or more additional predictors to add to your model and
##   repeat steps 1-3. Is this model significantly better than the model
##   with /metro/ as the only predictor?
## with metro, population, area, waste, toxic and green
```{r}
ex.me.mod2 <- lm(energy ~ metro + pop + area + waste + toxic + green, data = states.data)
summary(ex.me.mod2)
```


# Removed pop as it had the highest p value
```{r}
ex.me.mod3 <- lm(energy ~ metro + area + waste + toxic + green, data = states.data)
summary(ex.me.mod3)
```


# Removed waste as it had the higest p value
```{r}
ex.me.mod4 <- lm(energy ~ metro + area + toxic + green, data = states.data)
summary(ex.me.mod4)
```


# Removed metro as it had the higest p value
```{r}
ex.me.mod5 <- lm(energy ~ area + toxic + green, data = states.data)
summary(ex.me.mod5)
```


# Removed area as it had the higest p value
```{r}
ex.me.mod6 <- lm(energy ~ toxic + green, data = states.data)
summary(ex.me.mod6)
```


## Exercise: interactions and factors
## ────────────────────────────────────────

##   Use the states data set.

##   1. Add on to the regression equation that you created in exercise 1 by
##      generating an interaction term and testing the interaction.

```{r}
ex.me.mod6.tox.gre <- lm(energy ~ toxic*green, data = states.data)
coef(Summary(ex.me.mod6.tox.gre))
```

##   2. Try adding region to the model. Are there significant differences
##      across the four regions?

```{r}
ex.me.mod7 <- lm(energy ~ region + green + toxic, data = states.data)
summary(ex.me.mod7)
```

# Since the adjusted R squared value reduces and there are no stars assigned to P value for region, adding region does not seem to affect the dependable variable energy.

